---
title: "Transmission Type and Fuel economy"
author: "Wang Yihong"
date: "Saturday, June 21, 2014"
output: pdf_document
---

*Forgive me to use the packages, All I want are prettier tables.*

##Executive Summary

This report provides an analysis of relation between the transmission types(automatic vs manual) and MPG(miles per gallon).Methods include t test for two groups, linear regression and data visualization.Results show that, in this sample, compared to manual transmission cars, automatic cars consume less fuel on average.

##Descritive Statistics

```{r,message=FALSE,results='asis'}
library(stargazer);
stargazer(mtcars,title = "Summary Statistics",header=FALSE)
```
T test of `mpg` for automatic and manual cars:
```{r}
dif = t.test(mtcars$mpg[mtcars$am==0],mtcars$mpg[mtcars$am==1])
```
In average, automatic cars have lower `mpg` than  manual transmission cars. `r dif$estimate[1]` vs `r dif$estimate[2]`.The t statistic `r dif$statistic` indicates that the difference between the two group is significant at `r dif$p.value` level.

##Model Selection

I study the correlation table to determine the variables that are correlated to the dependent variable `mpg`. (I know I'm not supposed to use the packages, but I just want a prettier table. Actually, I can use `cor` and `cor.test` to check the correlation.)
```{r,warning=FALSE, message=FALSE, results='asis', prompt=FALSE, dpi=600}
#source("https://gist.github.com/nofacetou/42ed588f76b32a8e96ec/raw/CorTab.R")
#options(xtable.comment = FALSE)
source("CorTab.R")
require(xtable)
ct = xtable(corstarsl(mtcars),digits=3,caption = "Correlation Table")
#library(xlsx)
#write.xlsx(ct, "E:/ct.xlsx") 
#print(ct, type="html")
print(ct,comment=FALSE)
```
Then I use the backward selection to determine the final model(results are untabulated):
```{r,results='hide'}
summary(step(lm(data=mtcars,
                mpg~cyl+wt+hp+disp+drat+qsec+factor(vs)+factor(am)+gear+carb),
             direction="backward",test="F"))
```
The best model(has lowest AIC) I've got from the above results is:
```{r,message=FALSE,results='asis'}
fit <- lm(mpg ~ wt + qsec + factor(am), data = mtcars)
stargazer(fit,title="Regression Results", omit.stat=c("LL","ser","f"), no.space=TRUE,header=FALSE)
```
Then the average difference in `mpg` between the automatic transmission cars and manual transmission cars is `r fit$coefficients[4]`,at the same level of weight and 1/4 mile time.

```{r}
sumCoef <- summary(fit)$coefficients
sumCoef[4,1] + c(-1, 1) * qt(.975, df = fit$df) * sumCoef[4, 2]
```
With 95% confidence, I estimate that a manual transmission car consumes more fuel, from 0.04573 to 5.82594 mpg, compared to an automatic transmission car, given the same weight and 1/4 mile time.

--------
##Appendix

```{r}
boxplot(mpg~am,data=mtcars, names=c("automatic","manual"),
        ylab = "Miles/(US) gallon",main="MPG for different transmission")
```

###Model Diagnostic 

```{r}
qqnorm(residuals(fit))
qqline(residuals(fit))
```
The residuals for the model is approximately normally distributed.



